---
title: "WhtDisID_Github"
author: "doris dai"
date: "10/9/2019"
output: 
  github_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(multicon)
library(pander)
panderOptions('digits', 2)
library(readr)
library(knitr)
library(lavaan)
library(xtable)
library(emmeans)
library(ggpirate)


study1a_clean <- read_csv("/Users/Doris/Desktop/self-dehumanization&trump/R scripts/study1a_clean.csv")

study1b_clean <- read_csv("/Users/Doris/Desktop/self-dehumanization&trump/R scripts/study1b_clean.csv")

study2_clean <- read_csv("/Users/Doris/Desktop/self-dehumanization&trump/R scripts/study2_clean.csv")

studyPLT_clean <- read_csv("/Users/Doris/Desktop/self-dehumanization&trump/R scripts/studyPLT_clean.csv")
```

#Project Overview
Secured votes from 54% of White Americans——comprising 88% of his voter base——Trump’s 2016 presidential win has created a (mis)perception: Trump represents the majority of White Americans, and his statments represents the viewpoints of the majority of White Americans. This (mis)perceived representativeness of Trump linked White Americans as a group to discriminatory ideologies, via Trump’s sexist, racist, and xenophobic statements regarding marginalized group during and after his campaign. This public image of the White racial group arguably creates psychological tension for liberal-leaning Whites, whose personal ideologies tend to be pro-egalitarian and antithetical to the discriminatory ideologies (e.g., racism, xenophobia, White supremacy and sexism) associated with their racial ingroup. In this project, we explored how liberal-leaning Whites Americans contend with the current public image of their racial ingroup through negotiating their racial identity. We conceptualize this tension as a form of *group-image threat* (i.e., a threat to one’s self-concept that arises when faced with negative attributes of one’s ingroup), and hypothesized that this threat leads liberal-leaning (but not conservative-leaning) Whites to *disidentify* from their racial ingroup (**H1**), and such racial disidentification will be coupled with increased *intentions to advocate for racial equality* (**H2**).

To test these two hypotheses, we conducted 3 studies, with a total sample of 2,481 White Americans via Amazon Mechanical Turk across a one-year span (from 5/23/2018 to 4/17/2019). Studies 1a, 1b and 2 tested **H1**, and study 2 tested **H2**.

Below you can find the results. Refer to *WhtDisId_analysis.R* for codes used, which can be used for replication along with the redacted datasets. 

##Materials and Measures
###Example of manipulation
The following is an example of the materials that participants received in the actual threat and the high threat condition. Participants in the control condition received no information.
```{r, echo=FALSE}
#actual threat example
manipulation_actual <- data.frame(
  group = c("Agree", "Disagree"),
  value = c(34, 66)
)

actual_image <- ggplot(manipulation_actual, aes(x="", y=value, fill=group)) +
  geom_bar(width=1, stat="identity") +
  coord_polar("y", start=0) +
  geom_text(aes(label = paste0(round(value), "%")), position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values=c("#F6AE2D", "#999999")) +
  labs(x = NULL, y = NULL, fill = NULL, title = "Example of Materials in the Actual Threat Condition",subtitle="Percentage of White Americans who feel that \nPresident Trump's views accurately reflect \ntheir own beliefs and concerns.")+
  theme_classic() + theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5))

ggsave("actual_image.png",plot=actual_image,height=6, width = 6)

#high threat example
manipulation_high <- data.frame(
  group = c("Agree", "Disagree"),
  value = c(66, 34)
)

high_image <- ggplot(manipulation_high, aes(x="", y=value, fill=group)) +
  geom_bar(width=1, stat="identity") +
  coord_polar("y", start=0) +
  geom_text(aes(label = paste0(round(value), "%")), position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values=c("#F6AE2D", "#999999")) +
  labs(x = NULL, y = NULL, fill = NULL, title = "Example of Materials in the High Threat Condition", subtitle="Percentage of White Americans who feel that \nPresident Trump's views accurately reflect \ntheir own beliefs and concerns.")+
  theme_classic() + theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5))

ggsave("high_image.png",plot=high_image,height=6, width = 6)

```

###Dependent variables and measures
```{r echo=FALSE}
variables.table <- data.frame("No." = 1:6, "VariableNames" = c("Political orientation", "White disidentification", "Trump’s perceived representativeness", "Liberal group identification", "Individual Advocacy", "Policy Support"), "ShortdiscriptionofMeasurement" = c("Participants' personal political beliefs (1 = extremely conservative to 8 = extremely liberal)", "Participants' tendency to distance themselves from the White racial group (1 = Strongly disagree to 7 = Strongly agree)", "Agreement with the idea that Trump's comments represent viewpoints of the White racial group (1 = Strongly disagree to 7 = Strongly agree)", "Participants' tendency to view belonging to the liberal group as central to self-concepts (1 = Strongly disagree to 7 = Strongly agree)", "The likelihood that participants would put in personal effort to push for racial equality (1 = Strongly disagree to 7 = Strongly agree)", "Participants' support for policies designed to help racial minorities (1 = Strongly disagree to 7 = Strongly agree)"))

pander(variables.table, style = "rmarkdown",justify = c('left', 'left', 'left'), split.table=350)
```

#Study 1a

##Condition moderates the relation between political orientation and White disidentification

###Main moderation MLR models
Was the association between (liberal) and White disidentification stronger in the high threat condition than that in the actual threat condition?
```{r Study 1a, echo=FALSE}
study1a_clean$condition <- as.factor(study1a_clean$condition)
levels(study1a_clean$condition) <- c("Control", "Actual threat", "High threat") #rename levels of condition


study1a_relevel <- study1a_clean %>% 
  rename(condition_control = condition) %>% 
  mutate(condition_actual = factor(condition_control, levels=c("Actual threat", "Control", "High threat"))) %>%  #add a condition with actual threat condition as the reference level
  mutate(LibCon_centered = scale(LibCon, scale=F)) #mean-center political orientation so that intercept becomes meaningful
```

**Control Condition as the Reference Level**
```{r echo=FALSE}
#regression model 1 with control as the reference
study1a_lm_control <- lm(WhtDis_comp~LibCon_centered + condition_control + LibCon_centered*condition_control, data=study1a_relevel)

pander(study1a_lm_control, style = "rmarkdown", split.table = 200)
```

**Actual Threat Condition as the Reference Level (Study 1a)**
```{r echo=FALSE}
#regression model 2 with actual threat as the reference
study1a_lm_actual <- lm(WhtDis_comp~LibCon_centered + condition_actual + LibCon_centered*condition_actual, data=study1a_relevel)

pander(study1a_lm_actual, style = "rmarkdown", split.table = 200)
```

**Simple slopes for political orientation by condition**
```{r echo=FALSE}
#simple slope
emtrends(study1a_lm_control, ~ condition_control, var ="LibCon_centered")
```

**Findings**: Although liberal political orientation was associated with racial disidentification in all three conditions, the association between liberal political orientation and racial disidentification was the strongest when participants received information suggesting that Trump’s discriminatory comments represented the majority (vs minority or no information) of Whites. 

###Relatively liberal Whites *vs.* relatively conservative Whites
Did relatively liberal participants and relatively conservative participants reacted differently to information suggesting Trump represents White Americans? 

**Relatively liberal participants**
```{r echo=FALSE}
#end-point analysis
study1a_relevel$LibCon_above <- study1a_relevel$LibCon_centered - sd(study1a_relevel$LibCon_centered) #center 1SD above the mean, leaning liberal

study1a_relevel$LibCon_below <- study1a_relevel$LibCon_centered + sd(study1a_relevel$LibCon_centered) #center 1SD below the mean, leaning conservative 

#Relatively liberal participants
study1a_lm_control_above <- lm(WhtDis_comp~LibCon_above + condition_control + LibCon_above*condition_control, data=study1a_relevel) #among relatively liberal participants 

pander(study1a_lm_control_above, style = "rmarkdown", split.table = 200)

study1a_lm_actual_above <- lm(WhtDis_comp~LibCon_above + condition_actual + LibCon_above*condition_actual, data=study1a_relevel) #among relatively liberal participants

pander(study1a_lm_actual_above, style = "rmarkdown", split.table = 200)
```

**Relatively conservative participants**
```{r, echo=FALSE}
#Relatively conservative participants

study1a_lm_control_below <- lm(WhtDis_comp~LibCon_below + condition_control + LibCon_below*condition_control, data=study1a_relevel) #among relatively conservative participants

pander(study1a_lm_control_below, style = "rmarkdown", split.table = 200)


study1a_lm_actual_below <- lm(WhtDis_comp~LibCon_below + condition_actual + LibCon_below*condition_actual, data=study1a_relevel) #among relatively conservative participants

pander(study1a_lm_actual_below, style = "rmarkdown", split.table = 200)
```

**Findings**: Information suggesting that Trump’s discriminatory comments represents the majority (vs. minority) of White Americans led liberal-leaning Whites to disidentify from their racial group, while conservative-leaning Whites’ racial identities were not affected by information suggesting Trump’s representativeness

##Plot of political orientaion interacting with condition on White disidentification
```{r, echo=FALSE}
# regression graph
study1a.main <- ggplot(study1a_relevel, aes(x=LibCon, y=WhtDis_comp, group=condition_control)) +
  theme_bw() +
  geom_smooth(method=lm, aes(col=condition_control, linetype=condition_control, fill=condition_control), alpha=0.2) +
  scale_fill_manual(values = c("#E69F00","#009E73", "#56B4E9"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) +
  scale_color_manual(values = c("#E69F00","#009E73", "#56B4E9"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) +
  scale_linetype_manual(values=c("dashed", "dotted", "solid"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) + 
  theme(legend.title = element_blank())+
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8), limits=c(1, 8)) + 
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7),limits=c(1, 7)) + 
  geom_vline(xintercept = 2.830357, linetype = "dashed", size = .5) + 
  geom_vline(xintercept = 7.098513, linetype = "dashed", size = .5) + 
  annotate("text", x = 6.5, y = 4.8, label = "*", size = 6) +
  annotate("text", x = 6.5, y = 3.4, label = "*", size = 6) +
  annotate("text", x = 6.5, y = 4.1, label = "*", size = 6) +
  annotate("text", x = 1.3, y = 1, label = "extremely\nconservative", size = 3)+
  annotate("text", x = 7.9, y = 1, label = "extremely\nliberal", size = 3)+
  theme(text=element_text(size=12), legend.text=element_text(size=10)) +
  xlab("Political orientation") + ylab("Disidentification from the White racial group") +
  labs(title = "Relationship Between Racial Disidentification and \nPolitical Orientaion by Condition (Study 1a)", subtitle = "Note: Around each slope, 95% confidence bands are depicted. \n* denotes a statistically significant slope, p < .001. \nThe horizontal dashed lines refer to ±1SD from the mean of political belief orientation.")

ggsave("study1a.main.png",plot=study1a.main,height=6, width = 8)
```

# Study 1b
## Replication of Study 1a (MLR Model Testing)
###Manipulation check
The purpose of manipulation check is to check whether the high threat condition increased the extent to which participants perceived Trump to be representative of Whites, compared to the actual threat condition 
```{r study 1b, echo=FALSE}
study1b_relevel <- study1b_clean %>% 
  mutate(condition_actual = factor(condition, levels=c("Actual threat", "High threat"))) %>%  #add a condition with actual threat condition as the reference level
  mutate(LibCon_centered = scale(LibCon, scale=F)) #center political orientation

#manipulation check 

mancheck.study1a <- t.test(TrumpProto ~ condition, data = study1b_relevel) #whether condition affected participants' perceived Trump's representativeness of Whites

study1b.check <- ggplot(study1b_relevel, aes(x=condition, y=TrumpProto))+
   theme_bw() +
  geom_pirate(aes(col=condition, fill=condition))+
  scale_x_discrete(labels=c("Actual threat condition", "High threat condition")) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7),limits=c(1, 7)) + 
  ylab("Trump's Perceived Representativeness of Whites") + xlab("Condition") +
  labs(title = "Ratings of Trump's Perceived Representativeness of \nWhites by Condition (Study 2b)", subtitle="Note: Points represent the jittered raw data.\nBars represent central tendencies.\nBoxes represent 95% confidence interval.") +
  annotate("text", x = 1.5, y = 6.5, label = "*", size = 6) +
  annotate("text", x = 1.5, y = 6.2, label = "italic(p) < .001", size = 4, parse=T)

ggsave("study1b.check.png",plot=study1b.check,height=6, width = 8)
```

###Main moderation MLR testing
Was the association between (liberal) and White disidentification stronger in the high threat condition than that in the actual threat condition?

**Actual Condition as the Reference Level**
```{r echo=FALSE}

#regression
study1b_lm_actual <- lm(WhtDis_comp~ LibCon_centered + condition_actual + LibCon_centered*condition_actual, data=study1b_relevel)
pander(study1b_lm_actual, style = "rmarkdown", split.table = 200)
#confint(study1b_lm_actual)
```

**Simple slopes for political orientation by condition**
```{r echo=FALSE}
#simple slope
emtrends(study1b_lm_actual, ~ condition_actual, var ="LibCon_centered")
```

**Findings**: Consistent with Study 1a, the effect of liberal political orientation on racial disidentification was stronger when participants received information suggesting that Trump’s discriminatory comments represented the majority (vs. minority) of Whites.

###Relatively liberal Whites *vs.* relatively conservative Whites
Did relatively liberal participants and relatively conservative participants reacted differently to information suggesting Trump represents White Americans? 

**Relatively liberal participants**
```{r, echo=FALSE}
#end-point analysis
study1b_relevel$LibCon_above <- study1b_relevel$LibCon_centered - sd(study1b_relevel$LibCon_centered) #center 1SD above the mean, leaning liberal

study1b_relevel$LibCon_below <- study1b_relevel$LibCon_centered + sd(study1b_relevel$LibCon_centered) #center 1SD below the mean, leaning conservative

#Relatively liberal participants
study1b_lm_actual_above <- lm(WhtDis_comp~ LibCon_above + condition_actual + LibCon_above*condition_actual, data=study1b_relevel) #among relatively liberal participants

pander(study1b_lm_actual_above, style = "rmarkdown", split.table = 200)

#confint(study1b_lm_actual_above)
```

**Relatively conservative participants**
```{r, echo=FALSE}

study1b_lm_actual_below <- lm(WhtDis_comp~ LibCon_below + condition_actual + LibCon_below*condition_actual, data=study1b_relevel) #among relatively conservative participants

pander(study1b_lm_actual_below, style = "rmarkdown", split.table = 200)

#confint(study1b_lm_actual_below)
```

**Findings**: Consistent with Study 1a, compared to conservative-leaning participants, liberal-leaning participants’ racial identities were affected more strongly by the information that Trump represented the majority (vs. minority) of White Americans.

###Plot of Political Orientaion Interacting with Condition on White Disidentification
```{r, echo=FALSE}
# regression graph
study1b.main <- ggplot(study1b_clean, aes(x=LibCon, y=WhtDis_comp, group=condition)) +
  theme_bw() +
  geom_smooth(method=lm, aes(col=condition, linetype=condition, fill=condition), alpha=0.2) +
  scale_fill_manual(values = c("#009E73", "#56B4E9"), labels = c("Actual threat\ncondition","High threat\ncondition")) +
  scale_color_manual(values = c("#009E73", "#56B4E9"), labels = c("Actual threat\ncondition","High threat\ncondition")) +
  scale_linetype_manual(values=c("dotted", "solid"), labels = c("Actual threat\ncondition","High threat\ncondition")) + 
  theme(legend.title = element_blank())+
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8), limits=c(1, 8)) + 
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7),limits=c(1, 7)) + 
  geom_vline(xintercept = 2.657667, linetype = "dashed", size = .5) + 
  geom_vline(xintercept = 7.133378, linetype = "dashed", size = .5) + 
  annotate("text", x = 6.5, y = 5.4, label = "*", size = 6) +
  annotate("text", x = 6.5, y = 3.1, label = "*", size = 6) +
  annotate("text", x = 1.3, y = 1, label = "extremely\nconservative", size = 3)+
  annotate("text", x = 7.9, y = 1, label = "extremely\nliberal", size = 3)+
  theme(text=element_text(size=12), legend.text=element_text(size=10)) +
  xlab("Political orientation") + ylab("Disidentification from the White racial group") +
  labs(title = "Relationship Between Racial Disidentification and \nPolitical Orientaion by Condition (Study 1b)", subtitle = "Note: Around each slope, 95% confidence bands are depicted. \n* denotes a statistically significant slope, p < .001. \nThe horizontal dashed lines refer to ±1SD from the mean of political belief orientation.")

ggsave("study1b.main.png",plot=study1b.main,height=6, width = 8)
```

## Liberal Identification as Covariate (Alternative Explanation Testing)
```{r, echo=FALSE}
study1b_lm_alternative <- lm(WhtDis_comp ~ LibID + LibCon_centered + condition_actual + LibCon_centered*condition_actual, data=study1b_relevel) #covariate liberal identity

pander(study1b_lm_alternative, style = "rmarkdown", split.table = 200)
#confint(study1b_lm_alternative)
```

```{r multicollnearity, eval=FALSE, include=FALSE}
#test for multicollnearity
library(mctest)
omcdiag(study1b_relevel[,c(1,5)], study1b_relevel$WhtDis_comp)

imcdiag(study1b_relevel[,c(1,5)], study1b_relevel$WhtDis_comp)
```

**Findings**: The effect of group-image threat on racial disidentification occurred above and beyond liberal group identification. However, these results should be considered with caution because political orientation and liberal identification are correlated.


#Study 2
##Replication of Study 1a (MLR Model Testing)
###Manipulation check
The purpose of manipulation check is to check whether the high threat condition increased the extent to which participants perceived Trump to be representative of Whites, compared to the actual threat condition 
```{r study 2, echo=FALSE}
study2_clean$condition <- as.factor(study2_clean$condition)
study2_clean$condition <- factor(study2_clean$condition, levels = c("Control", "Actual threat","High threat"))

study2_relevel <- study2_clean %>% 
  rename(condition_control = condition) %>% 
  mutate(condition_actual = factor(condition_control, levels=c("Actual threat", "Control", "High threat"))) %>%  #add a condition with actual threat condition as the reference level
  mutate(LibCon_centered = scale(LibCon, scale=F))

study2_contrast <- study2_relevel %>% 
  filter(condition_actual == "Actual threat" | condition_actual == "High threat")

mancheck.study2 <- t.test(TrumpProto ~ condition_actual, data = study2_contrast)

study2.check <- ggplot(study2_contrast, aes(x=condition_actual, y=TrumpProto))+
   theme_bw() +
  geom_pirate(aes(col=condition_actual, fill=condition_actual))+
  scale_x_discrete(labels=c("Actual threat condition", "High threat condition")) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7),limits=c(1, 7)) + 
  ylab("Trump's Perceived Representativeness of Whites") + xlab("Condition") +
  labs(title = "Ratings of Trump's Perceived Representativeness of \nWhites by Condition (Study 2)", subtitle="Note: Points represent the jittered raw data.\nBars represent central tendencies.\nBoxes represent 95% confidence interval.")+
    annotate("text", x = 1.5, y = 6.5, label = "*", size = 6) +
  annotate("text", x = 1.5, y = 6.2, label = "italic(p) < .001", size = 4, parse=T)

ggsave("study2.check.png",plot=study2.check,height=6, width = 8)
```

###Main moderation MLR testing
Was the association between (liberal) and White disidentification stronger in the high threat condition than that in the actual threat condition?

**Control Condition as the Reference Level**
```{r echo=FALSE}
#replication of Study 1a
#regression model 1 with control as the reference
study2_lm_control <- lm(WhtDis_comp~LibCon_centered + condition_control + LibCon_centered*condition_control, data=study2_relevel)

pander(study2_lm_control, style = "rmarkdown", split.table = 200)
#confint(study2_lm_control)
```

**Actual Threat Condition as the Reference Level**
```{r echo=FALSE}
#regression model 2 with actual threat as the reference
study2_lm_actual <- lm(WhtDis_comp~LibCon_centered + condition_actual + LibCon_centered*condition_actual, data=study2_relevel)

pander(study2_lm_actual, style = "rmarkdown", split.table = 200)
#confint(study2_lm_actual)
```

**Simple slopes for political orientation by condition**
```{r echo=FALSE}
#simple slope
emtrends(study2_lm_control, ~ condition_control, var ="LibCon_centered")
```

**Findings**: Consistent with Studies 1a and 1b, the effect of liberal political orientation on racial disidentification was stronger when participants received information suggesting that Trump’s discriminatory comments represented the majority of Whites than when receiving information suggesting that Trump’s comments only represented the minority of Whites. 

###Relatively liberal Whites *vs.* relatively conservative Whites
Did relatively liberal participants and relatively conservative participants reacted differently to information suggesting Trump represents White Americans? 

**Relatively liberal participants**
```{r echo=FALSE}
#end-point analysis
study2_relevel$LibCon_above <- study2_relevel$LibCon_centered - sd(study2_relevel$LibCon_centered) #center 1SD above the mean, leaning liberal

study2_relevel$LibCon_below <- study2_relevel$LibCon_centered + sd(study2_relevel$LibCon_centered) #center 1SD below the mean, leaning conservative 

#Relatively liberal participants
study2_lm_control_above <- lm(WhtDis_comp~LibCon_above + condition_control + LibCon_above*condition_control, data=study2_relevel) #among relatively liberal participants 

pander(study2_lm_control_above, style = "rmarkdown", split.table = 200)

study2_lm_actual_above <- lm(WhtDis_comp~LibCon_above + condition_actual + LibCon_above*condition_actual, data=study2_relevel) #among relatively liberal participants

pander(study2_lm_actual_above, style = "rmarkdown", split.table = 200)
```

**Relatively conservative participants**
```{r, echo=FALSE}
#Relatively conservative participants

study2_lm_control_below <- lm(WhtDis_comp~LibCon_below + condition_control + LibCon_below*condition_control, data=study2_relevel) #among relatively conservative participants

pander(study2_lm_control_below, style = "rmarkdown", split.table = 200)

study2_lm_actual_below <- lm(WhtDis_comp~LibCon_below + condition_actual + LibCon_below*condition_actual, data=study2_relevel) #among relatively conservative participants

pander(study2_lm_actual_below, style = "rmarkdown", split.table = 200)
```

**Findings**: Consistent with Studies 1a and 1b, receiving information suggesting that Trump’s discriminatory comments represented the majority (vs. minority) of White Americans led liberal-leaning Whites to disidentify from their racial group, while conservative-leaning Whites’ racial identities were not affected by information suggesting Trump’s representativeness.

###Plot of Political Orientaion Interacting with Condition on White Disidentification
```{r, echo=FALSE}
# regression graph
study2.main <- ggplot(study2_relevel, aes(x=LibCon, y=WhtDis_comp, group=condition_control)) +
  theme_bw() +
  geom_smooth(method=lm, aes(col=condition_control, linetype=condition_control, fill=condition_control), alpha=0.2) +
  scale_fill_manual(values = c("#E69F00","#009E73", "#56B4E9"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) +
  scale_color_manual(values = c("#E69F00","#009E73", "#56B4E9"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) +
  scale_linetype_manual(values=c("dashed", "dotted", "solid"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) + 
  theme(legend.title = element_blank())+
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8), limits=c(1, 8)) + 
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7),limits=c(1, 7)) + 
  geom_vline(xintercept = 2.830357, linetype = "dashed", size = .5) + 
  geom_vline(xintercept = 7.098513, linetype = "dashed", size = .5) + 
  annotate("text", x = 6.5, y = 4.8, label = "*", size = 6) +
  annotate("text", x = 6.5, y = 3.3, label = "*", size = 6) +
  annotate("text", x = 6.5, y = 4.2, label = "*", size = 6) +
  annotate("text", x = 1.3, y = 1, label = "extremely\nconservative", size = 3)+
  annotate("text", x = 7.9, y = 1, label = "extremely\nliberal", size = 3)+
  theme(text=element_text(size=12), legend.text=element_text(size=10)) +
  xlab("Political orientation") + ylab("Disidentification from the White racial group") +
  labs(title = "Relationship Between Racial Disidentification and \nPolitical Orientaion by Condition (Study 2)", subtitle = "Note: Around each slope, 95% confidence bands are depicted. \n* denotes a statistically significant slope, p < .001. \nThe horizontal dashed lines refer to ±1SD from the mean of political belief orientation.")

ggsave("study2.main.png",plot=study2.main,height=6, width = 8)
```

##Implications of Racial Disidentification for Racial Equity
Note: b1a3 = Index of moderated mediation, (a1b1+b1a3 -1) and (a1b1+b1a3 1) = conditional indirect effects 
```{r echo=FALSE}
#test using lavaan

#compute interaction terms
study2_contrast_mod <- study2_contrast %>% 
  mutate(condition_contrast = ifelse(condition_actual == "Actual threat", -1, 1)) %>% 
  mutate(WhtDis_comp_centered = scale(WhtDis_comp, scale=F)) %>% 
  mutate(LibCon_condition = LibCon_centered * condition_contrast,
         DisId_condition = WhtDis_comp_centered * condition_contrast)
#head(study2_contrast,5)
#tail(study2_contrast,5)
```

**Individual advocacy for racial equity**
```{r echo=FALSE}
#individual support

mod_IndivAct <- " #a path
WhtDis_comp_centered ~ 1 + a1 * LibCon_centered
WhtDis_comp_centered ~ a2 * condition_contrast
WhtDis_comp_centered ~ a3 * LibCon_condition

# b path
IndivAction ~ b1 * WhtDis_comp_centered

# c prime path
IndivAction ~ 1 + cp * LibCon_centered

# index of moderated mediation and conditional indirect effects
b1a3 := b1 * a3
actualss := a1 + a3 * -1
highss := a1 + a3 * 1
actual := a1 * b1 + b1a3 * -1
high := a1 * b1 + b1a3 * 1"

set.seed(1234)

sem.fit_IndivAct <- sem(mod_IndivAct, data = study2_contrast_mod, se = "bootstrap", bootstrap = 5000, likelihood = "wishart")

para_IndivAct <- parameterestimates(sem.fit_IndivAct, boot.ci.type = "bca.simple", standardized = TRUE) 

pander(para_IndivAct, style = "rmarkdown", split.table = 200) #print results
```

**Support for policies designed to help racially minoritized groups**
```{r echo=FALSE}
#policy support
mod_PolicySupport <- " #a path
WhtDis_comp_centered ~ 1 + a1 * LibCon_centered
WhtDis_comp_centered ~ a2 * condition_contrast
WhtDis_comp_centered ~ a3 * LibCon_condition

# b path
PolicySupport ~ b1 * WhtDis_comp_centered

# c prime path
PolicySupport ~ 1 + cp * LibCon_centered

# index of moderated mediation and conditional indirect effects
b1a3 := b1 * a3
actualss := a1 + a3 * -1
highss := a1 + a3 * 1
actual := a1 * b1 + b1a3 * -1
high := a1 * b1 + b1a3 * 1"

set.seed(1234)

sem.fit_PolicySupport <- sem(mod_PolicySupport, data = study2_contrast_mod, se = "bootstrap", bootstrap = 5000, likelihood = "wishart")

para_policy <- parameterestimates(sem.fit_PolicySupport, boot.ci.type = "bca.simple", standardized = TRUE) 

pander(para_policy, style = "rmarkdown", split.table = 200)
```

**Findings**: Among participants who learned that Trump’s comments represented the majority (vs. minority) of Whites, liberal political orientation had a stronger effect on racial disidentification, which further had a stronger effect on intentions to advocate for racial equality through individual advocacy and policy support.
