---
title: "WhtDisID_Github"
author: "doris dai"
date: "10/9/2019"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(multicon)
library(pander)
library(readr)
library(knitr)
library(lavaan)
library(xtable)
library(emmeans)


################load data
```

#Project Overview
Secured votes from 54% of White Americans——comprising 88% of his voter base——Trump’s 2016 presidential win has created a (mis)perception: Trump represents the majority of White Americans, and his statments represents the viewpoints of the majority of White Americans. This (mis)perceived representativeness of Trump linked White Americans as a group to discriminatory ideologies, via Trump’s sexist, racist, and xenophobic statements regarding marginalized group during and after his campaign. This public image of the White racial group arguably creates psychological tension for liberal-leaning Whites, whose personal ideologies tend to be pro-egalitarian and antithetical to the discriminatory ideologies (e.g., racism, xenophobia, White supremacy and sexism) associated with their racial ingroup. In this project, we explored how liberal-leaning Whites Americans contend with the current public image of their racial ingroup through negotiating their racial identity. We conceptualize this tension as a form of *group-image threat* (i.e., a threat to one’s self-concept that arises when faced with negative attributes of one’s ingroup), and hypothesized that this threat leads liberal-leaning (but not conservative-leaning) Whites to *disidentify* from their racial ingroup (**H1**), and such racial disidentification will be coupled with increased *intentions to advocate for racial equality* (**H2**).

To test these two hypotheses, we conducted 3 studies, with a total sample of 2,481 White Americans via Amazon Mechanical Turk across a one-year span (from 5/23/2018 to 4/17/2019). Studies 1a, 1b and 2 tested **H1**, and study 2 tested **H2**.

Below you can find the results. Refer to *WhtDisId_analysis.R* for codes used, which can be used for replication along with the redacted datasets. 

##Variables and Measures
```{r echo=FALSE}
variables.table <- data.frame("No." = 1:6, "VariableNames" = c("Political orientation", "White disidentification", "Trump’s perceived representativeness", "Liberal group identification", "Individual Advocacy", "Policy Support"), "ShortdiscriptionofMeasurement" = c("Participants' personal political beliefs (1 = extremely conservative to 8 = extremely liberal)", "Participants' tendency to distance themselves from the White racial group (1 = Strongly disagree to 7 = Strongly agree)", "Agreement with the idea that Trump's comments represent viewpoints of the White racial group (1 = Strongly disagree to 7 = Strongly agree)", "Participants' tendency to view belonging to the liberal group as central to self-concepts (1 = Strongly disagree to 7 = Strongly agree)", "The likelihood that participants would put in personal effort to push for racial equality (1 = Strongly disagree to 7 = Strongly agree)", "Participants' support for policies designed to help racial minorities (1 = Strongly disagree to 7 = Strongly agree)"))

pander(variables.table, style = "rmarkdown",justify = c('left', 'left', 'left'), split.table=350)
```

#Study 1a

##condition moderates the relation between political orientation and White disidentification (MLR Model Testing)

###Main moderation MLR models
```{r Study 1a, echo=FALSE}
#RELOAD STUDY 1A, ADD TRUMP PROTO

study1a_clean$condition <- as.factor(study1a_clean$condition)
levels(study1a_clean$condition) <- c("Control", "Actual threat", "High threat") #rename levels of condition


study1a_relevel <- study1a_clean %>% 
  rename(condition_control = condition) %>% 
  mutate(condition_actual = factor(condition_control, levels=c("Actual threat", "Control", "High threat"))) %>%  #add a condition with actual threat condition as the reference level
  mutate(LibCon_centered = scale(LibCon, scale=F)) #mean-center political orientation so that intercept becomes meaningful

  
#regression model 1 with control as the reference
study1a_lm_control <- lm(WhtDis_comp~LibCon_centered + condition_control + LibCon_centered*condition_control, data=study1a_relevel)

kable(xtable(study1a_lm_control), caption="Control Condition as the Reference Level (Study 1a)")

#regression model 2 with actual threat as the reference
study1a_lm_actual <- lm(WhtDis_comp~LibCon_centered + condition_actual + LibCon_centered*condition_actual, data=study1a_relevel)

kable(xtable(study1a_lm_actual), caption="Actual Threat Condition as the Reference Level (Study 1a)")
```

Simple slopes for political orientation by condition
```{r echo=FALSE}
#simple slope
emtrends(study1a_lm_control, ~ condition_control, var ="LibCon_centered")

```

###Relatively liberal Whites *vs.* relatively conservative Whites
```{r echo=FALSE}
#end-point analysis
study1a_relevel$LibCon_above <- study1a_relevel$LibCon_centered - sd(study1a_relevel$LibCon_centered) #center 1SD above the mean, leaning liberal

study1a_relevel$LibCon_below <- study1a_relevel$LibCon_centered + sd(study1a_relevel$LibCon_centered) #center 1SD below the mean, leaning conservative 

#model 1
study1a_lm_control_above <- lm(WhtDis_comp~LibCon_above + condition_control + LibCon_above*condition_control, data=study1a_relevel) #among relatively liberal participants 
kable(xtable(study1a_lm_control_above), caption="Control Condition as the Reference Level among Relatively Liberal Participants (Study 1a)")

study1a_lm_control_below <- lm(WhtDis_comp~LibCon_below + condition_control + LibCon_below*condition_control, data=study1a_relevel) #among relatively conservative participants

kable(xtable(study1a_lm_control_below), caption="Control Condition as the Reference Level among Relatively Conservative Participants (Study 1a)")

#model 2
study1a_lm_actual_above <- lm(WhtDis_comp~LibCon_above + condition_actual + LibCon_above*condition_actual, data=study1a_relevel) #among relatively liberal participants

kable(xtable(study1a_lm_actual_above), caption="Actual Condition as the Reference Level among Relatively Liberal Participants (Study 1a)")

study1a_lm_actual_below <- lm(WhtDis_comp~LibCon_below + condition_actual + LibCon_below*condition_actual, data=study1a_relevel) #among relatively conservative participants

kable(xtable(study1a_lm_actual_below), caption="Actual Condition as the Reference Level among Relatively Conservative Participants (Study 1a)")
```

##Plot of Political Orientaion Interacting with Condition on White Disidentification
```{r, echo=FALSE}
# regression graph
ggplot(study1a_relevel, aes(x=LibCon, y=WhtDis_comp, group=condition_control)) +
  theme_bw() +
  geom_smooth(method=lm, aes(col=condition_control, linetype=condition_control, fill=condition_control), alpha=0.2) +
  scale_fill_manual(values = c("#E69F00","#009E73", "#56B4E9"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) +
  scale_color_manual(values = c("#E69F00","#009E73", "#56B4E9"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) +
  scale_linetype_manual(values=c("dashed", "dotted", "solid"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) + 
  theme(legend.title = element_blank())+
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8), limits=c(1, 8)) + 
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7),limits=c(1, 7)) + 
  geom_vline(xintercept = 2.830357, linetype = "dashed", size = .5) + 
  geom_vline(xintercept = 7.098513, linetype = "dashed", size = .5) + 
  annotate("text", x = 6.5, y = 4.8, label = "*", size = 6) +
  annotate("text", x = 6.5, y = 3.4, label = "*", size = 6) +
  annotate("text", x = 6.5, y = 4.1, label = "*", size = 6) +
  annotate("text", x = 1.3, y = 1, label = "extremely\nconservative", size = 3)+
  annotate("text", x = 7.9, y = 1, label = "extremely\nliberal", size = 3)+
  theme(text=element_text(size=12), legend.text=element_text(size=10)) +
  xlab("Political orientation") + ylab("Disidentification from the White racial group") +
  labs(title = "Relationship Between Racial Disidentification and \nPolitical Orientaion by Condition (Study 1a)")
```

# Study 1b
## Replication of Study 1a (MLR Model Testing)

###Main moderation MLR testing
```{r study 1b, echo=FALSE}
study1b_clean$condition <- as.factor(study1b_clean$condition)

levels(study1b_clean$condition) <- c("High threat","Actual threat")

study1b_relevel <- study1b_clean %>% 
  mutate(condition_actual = factor(condition, levels=c("Actual threat", "High threat"))) %>%  #add a condition with actual threat condition as the reference level
  mutate(LibCon_centered = scale(LibCon, scale=F)) #center political orientation

#regression
study1b_lm_actual <- lm(WhtDis_comp~ LibCon_centered + condition_actual + LibCon_centered*condition_actual, data=study1b_relevel)
summary(study1b_lm_actual)
kable(xtable(study1b_lm_actual), caption="Actual Condition as the Reference Level (Study 1b)")
```

Simple slopes for political orientation by condition
```{r echo=FALSE}
#simple slope
emtrends(study1b_lm_actual, ~ condition_actual, var ="LibCon_centered")
```

###Relatively liberal Whites *vs.* relatively conservative Whites

```{r, echo=FALSE}
#end-point analysis
study1b_relevel$LibCon_above <- study1b_relevel$LibCon_centered - sd(study1b_relevel$LibCon_centered) #center 1SD above the mean, leaning liberal

study1b_relevel$LibCon_below <- study1b_relevel$LibCon_centered + sd(study1b_relevel$LibCon_centered) #center 1SD below the mean, leaning conservative

study1b_lm_actual_above <- lm(WhtDis_comp~ LibCon_above + condition_actual + LibCon_above*condition_actual, data=study1b_relevel) #among relatively liberal participants

kable(xtable(study1b_lm_actual_above), caption="Actual Condition as the Reference Level among Relatively Liberal Participants (Study 1b)")

study1b_lm_actual_below <- lm(WhtDis_comp~ LibCon_below + condition_actual + LibCon_below*condition_actual, data=study1b_relevel) #among relatively conservative participants

kable(xtable(study1b_lm_actual_below), caption = "Actual Condition as the Reference Level among Relatively Conservative Participants (Study 1b)")
```

##Plot of Political Orientaion Interacting with Condition on White Disidentification
```{r, echo=FALSE}
# regression graph
ggplot(study1b_clean, aes(x=LibCon, y=WhtDis_comp, group=condition)) +
  theme_bw() +
  geom_smooth(method=lm, aes(col=condition, linetype=condition, fill=condition), alpha=0.2) +
  scale_fill_manual(values = c("#009E73", "#56B4E9"), labels = c("Actual threat\ncondition","High threat\ncondition")) +
  scale_color_manual(values = c("#009E73", "#56B4E9"), labels = c("Actual threat\ncondition","High threat\ncondition")) +
  scale_linetype_manual(values=c("dotted", "solid"), labels = c("Actual threat\ncondition","High threat\ncondition")) + 
  theme(legend.title = element_blank())+
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8), limits=c(1, 8)) + 
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7),limits=c(1, 7)) + 
  geom_vline(xintercept = 2.657667, linetype = "dashed", size = .5) + 
  geom_vline(xintercept = 7.133378, linetype = "dashed", size = .5) + 
  annotate("text", x = 6.5, y = 5.4, label = "*", size = 6) +
  annotate("text", x = 6.5, y = 3.1, label = "*", size = 6) +
  annotate("text", x = 1.3, y = 1, label = "extremely\nconservative", size = 3)+
  annotate("text", x = 7.9, y = 1, label = "extremely\nliberal", size = 3)+
  theme(text=element_text(size=12), legend.text=element_text(size=10)) +
  xlab("Political orientation") + ylab("Disidentification from the White racial group") +
  labs(title = "Relationship Between Racial Disidentification and \nPolitical Orientaion by Condition (Study 1b)")
```

## Liberal Identification as Covariate (Alternative Explanation Testing)
```{r, echo=FALSE}
study1b_lm_alternative <- lm(WhtDis_comp ~ LibId_comp + LibCon_centered + condition_actual + LibCon_centered*condition_actual, data=study1b_relevel) #covariate liberal identity

kable(xtable(study1b_lm_alternative), caption = "Effect of Political Orientation and Condition Above and Beyond Liberal Identification")
```

```{r multicollnearity, eval=FALSE, include=FALSE}
#test for multicollnearity
library(mctest)
omcdiag(study1b_relevel[,c(1,5)], study1b_relevel$WhtDis_comp)

imcdiag(study1b_relevel[,c(1,5)], study1b_relevel$WhtDis_comp)
```


#Study 2
##Replication of Study 1a (MLR Model Testing)
```{r study 2, echo=FALSE}

study2_clean$condition <- as.factor(study2_clean$condition)
study2_clean$condition <- factor(study2_clean$condition, levels = c("Control", "Actual threat","High threat"))



study2_relevel <- study2_clean %>% 
  rename(condition_control = condition) %>% 
  mutate(condition_actual = factor(condition_control, levels=c("Actual threat", "Control", "High threat"))) %>%  #add a condition with actual threat condition as the reference level
  mutate(LibCon_centered = scale(LibCon, scale=F))
  
study2_relevel$condition_control <- as.factor(study2_relevel$condition_control)

#replication of Study 1a
#regression model 1 with control as the reference
study2_lm_control <- lm(WhtDis_comp~LibCon_centered + condition_control + LibCon_centered*condition_control, data=study2_relevel)

kable(xtable(study2_lm_control), caption = "Control Condition as the Reference Level (Study 2)")

#regression model 2 with actual threat as the reference
study2_lm_actual <- lm(WhtDis_comp~LibCon_centered + condition_actual + LibCon_centered*condition_actual, data=study2_relevel)

kable(xtable(study2_lm_actual), caption = "Actual Threat Condition as the Reference Level (Study 2)")
```

Simple slopes for political orientation by condition
```{r echo=FALSE}
#simple slope
emtrends(study2_lm_control, ~ condition_control, var ="LibCon_centered")
```

###Relatively liberal Whites *vs.* relatively conservative Whites

```{r echo=FALSE}
#end-point analysis
study2_relevel$LibCon_above <- study2_relevel$LibCon_centered - sd(study2_relevel$LibCon_centered) #center 1SD above the mean, leaning liberal

study2_relevel$LibCon_below <- study2_relevel$LibCon_centered + sd(study2_relevel$LibCon_centered) #center 1SD below the mean, leaning conservative 

#model 1
study2_lm_control_above <- lm(WhtDis_comp~LibCon_above + condition_control + LibCon_above*condition_control, data=study2_relevel) #among relatively liberal participants 

kable(xtable(study2_lm_control_above), caption="Control Condition as the Reference Level among Relatively Liberal Participants (Study 2)")

study2_lm_control_below <- lm(WhtDis_comp~LibCon_below + condition_control + LibCon_below*condition_control, data=study2_relevel) #among relatively conservative participants

kable(xtable(study2_lm_control_below), caption="Control Condition as the Reference Level among Relatively Conservative Participants (Study 2)")

#model 2
study2_lm_actual_above <- lm(WhtDis_comp~LibCon_above + condition_actual + LibCon_above*condition_actual, data=study2_relevel) #among relatively liberal participants

kable(xtable(study2_lm_actual_above), caption="Actual Condition as the Reference Level among Relatively Liberal Participants (Study 2)")

study2_lm_actual_below <- lm(WhtDis_comp~LibCon_below + condition_actual + LibCon_below*condition_actual, data=study2_relevel) #among relatively conservative participants

kable(xtable(study2_lm_actual_below),  caption="Actual Condition as the Reference Level among Relatively Conservative Participants")
```

##Plot of Political Orientaion Interacting with Condition on White Disidentification
```{r, echo=FALSE}
# regression graph
ggplot(study2_relevel, aes(x=LibCon, y=WhtDis_comp, group=condition_control)) +
  theme_bw() +
  geom_smooth(method=lm, aes(col=condition_control, linetype=condition_control, fill=condition_control), alpha=0.2) +
  scale_fill_manual(values = c("#E69F00","#009E73", "#56B4E9"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) +
  scale_color_manual(values = c("#E69F00","#009E73", "#56B4E9"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) +
  scale_linetype_manual(values=c("dashed", "dotted", "solid"), labels = c("Control condition", "Actual threat\ncondition", "High threat\ncondition")) + 
  theme(legend.title = element_blank())+
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8), limits=c(1, 8)) + 
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7),limits=c(1, 7)) + 
  geom_vline(xintercept = 2.830357, linetype = "dashed", size = .5) + 
  geom_vline(xintercept = 7.098513, linetype = "dashed", size = .5) + 
  annotate("text", x = 6.5, y = 4.8, label = "*", size = 6) +
  annotate("text", x = 6.5, y = 3.4, label = "*", size = 6) +
  annotate("text", x = 6.5, y = 4.1, label = "*", size = 6) +
  annotate("text", x = 1.3, y = 1, label = "extremely\nconservative", size = 3)+
  annotate("text", x = 7.9, y = 1, label = "extremely\nliberal", size = 3)+
  theme(text=element_text(size=12), legend.text=element_text(size=10)) +
  xlab("Political orientation") + ylab("Disidentification from the White racial group") +
  labs(title = "Relationship Between Racial Disidentification and \nPolitical Orientaion by Condition (Study 2)")
```

##Implications of Racial Disidentification for Racial Equity

Note: b1a3 = Index of moderated mediation, (a1b1+b1a3 -1) and (a1b1+b1a3 1) = conditional indirect effects 
```{r echo=FALSE}
#test using lavaan

#compute interaction terms
study2_contrast <- study2_relevel %>% 
  filter(condition_actual == "Actual threat" | condition_actual == "High threat") %>% 
  mutate(condition_contrast = ifelse(condition_actual == "Actual threat", -1, 1)) %>% 
  mutate(WhtDis_comp_centered = scale(WhtDis_comp, scale=F)) %>% 
  mutate(LibCon_condition = LibCon_centered * condition_contrast,
         DisId_condition = WhtDis_comp_centered * condition_contrast)
#head(study2_contrast,5)
#tail(study2_contrast,5)

#individual support
mod_IndivAct <- " #a path
WhtDis_comp_centered ~ 1 + a1 * LibCon_centered
WhtDis_comp_centered ~ a2 * condition_contrast
WhtDis_comp_centered ~ a3 * LibCon_condition

# b path
IndivAction ~ b1 * WhtDis_comp_centered

# c prime path
IndivAction ~ 1 + cp * LibCon_centered

# index of moderated mediation and conditional indirect effects
b1a3 := b1 * a3
actualss := a1 + a3 * -1
highss := a1 + a3 * 1
actual := a1 * b1 + b1a3 * -1
high := a1 * b1 + b1a3 * 1"

set.seed(1234)

sem.fit_IndivAct <- sem(mod_IndivAct, data = study2_contrast, se = "bootstrap", bootstrap = 5000, likelihood = "wishart")

para_IndivAct <- parameterestimates(sem.fit_IndivAct, boot.ci.type = "bca.simple", standardized = TRUE) 

kable(xtable(para_IndivAct), caption = "Moderated Mediation with DV as Individual Action") #print results


#policy support
mod_PolicySupport <- " #a path
WhtDis_comp_centered ~ 1 + a1 * LibCon_centered
WhtDis_comp_centered ~ a2 * condition_contrast
WhtDis_comp_centered ~ a3 * LibCon_condition

# b path
PolicySupport ~ b1 * WhtDis_comp_centered

# c prime path
PolicySupport ~ 1 + cp * LibCon_centered

# index of moderated mediation and conditional indirect effects
b1a3 := b1 * a3
actualss := a1 + a3 * -1
highss := a1 + a3 * 1
actual := a1 * b1 + b1a3 * -1
high := a1 * b1 + b1a3 * 1"

set.seed(1234)

sem.fit_PolicySupport <- sem(mod_PolicySupport, data = study2_contrast, se = "bootstrap", bootstrap = 5000, likelihood = "wishart")

para_policy <- parameterestimates(sem.fit_PolicySupport, boot.ci.type = "bca.simple", standardized = TRUE) 

kable(xtable(para_policy), caption="Moderated Mediation with DV as Policy Support") #print results

```

